Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-14 snapshot_system/snapshot.tex
Added some initial data files for block<-snapshot links, and a couple paragraphs to failover.tex on how the empirical results support the model.
update cds analysis

\subsection{Inner and corss VM deduplication}

@@

For the Zipf-like distribution, an approximation to the sum of the first $n$ 
elements of the distribution can be derived as follows:
\begin{equation}
\sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
\end{equation}

So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
of global index with size $S_g$ is:

\begin{equation}
  E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
\end{equation}

%[Describe the dedup efficiency model in detail]
Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. Then $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}

By replacing $S_c$ and $S_g$ in the first formula, the deduplication efficiency becomes:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.

>>>>

\subsection{Inner and cross VM deduplication}

@@

Let $b$ be the total amount of data blocks after localized deduplication, $b_u$ be the total amount of fingerprints 
in the global index after complete deduplication, $C_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution we know an fingerprint's frequency is inversely proportional to its rank:
\begin{equation*}
C_i = X\frac{1}{i^\alpha},\; \sum_{i=1}^{b_u}C_i = X\sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
\end{equation*}

Thus $C_i$ can be expressed as:
\begin{equation}
C_i=\frac{b(1-\alpha)}{b_u^{1-\alpha}i^\alpha}
\end{equation}

We define deduplication efficiency $e$ to be the proportion of raw data that can be deduplicated,
In complete deduplication scenario, it deduplication efficiency $e_c$ is:
\begin{equation}
e_c = \frac{b-b_u}{b} = 1 - \frac{b_u}{b}
\end{equation}

If we only select the top $k$ most popular fingerprints from global index and remove only their duplicates,
the deduplication efficiency will be:
\begin{equation}
\begin{split}
e_k &= (\sum_{i=1}^{k}C_i - k)/{b} = (b * \frac{1-\alpha}{b_u^{1-\alpha}} * \sum_{i=1}^{k}\frac{1}{i^\alpha} - k)/b \\
%&\approx \frac{b*\frac{1-\alpha}{b_u^{1-\alpha}}*\frac{k^{1-alpha}}{1-\alpha} - k}{b}
&\approx (\frac{k}{b_u})^{1-\alpha} - \frac{k}{b} \approx (\frac{k}{b_u})^{1-\alpha},\; (since\; k \ll b)
\end{split}
\end{equation}

% For the Zipf-like distribution, an approximation to the sum of the first $n$ 
% elements of the distribution can be derived as follows:
% \begin{equation}
% \sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
% \end{equation}

% So the cumulative distribution function for a CDS holding top $S_c$ fingerprints
% of global index with size $S_g$ is:

% \begin{equation}
%   E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
% \end{equation}

%[Describe the dedup efficiency model in detail]
Let $N$ be the number of nodes in the cluster, $m$ be the memory on each node used by CDS, 
$F$ be the size of an CDS index entry,
$D$ be the amount of unique data on each node, and $B$ be the average block size. Then $k$ and $b_u$ can be expressed as:
\begin{equation*}
k = N*m/F,\; b_u = N*D/B
\end{equation*}

Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
\begin{equation}
  e_k = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of CDS is mainly affected by the its memory usage,
and the Zipf-like distribution parameter $\alpha$.
From the memory usage perspective, the more memory we give to CDS index, the more duplicates it can found.
From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
$\alpha$ would be small and thus CDS approach would not be effective. But in a VM cluster all VMs
have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
the better deduplication efficiency our CDS deduplication approach will have.
